\section*{Abstract}

%Linux socket is implemented in the kernel space with shared data structures that needs concurrency protection, which incurs significant overhead.
Communication intensive applications in hosts with multi-core CPU and high speed networking hardware often put considerable stress on the native socket system in an OS. 
Existing socket replacements often leave significant performance on the table, as well have limitations on compatibility and isolation.
%Communication intensive applications on modern computers with multi-core CPU and high-speed networking hardware 
%often put considerable stress on traditional socket implementation. 
%This design incurs significant kernel crossing and locking overhead.
%Recent user-space sockets often do not support intra-host communication among containers and applications, or have limitations on compatibility, isolation and scalability with multiple threads and concurrent connections.

%In this paper, we describe \sys{}, a high performance socket system that is fully compatible with Linux and can be used as a drop-in replacement with no modification to applications.
%\sys{} is implemented in user space to avoid kernel crossing cost and simplify deployment.
%Each host runs a monitor daemon to securely process the control plane, while the data plane bypasses the monitor.
%We achieve multi-thread scalability by considering threads as a shared-nothing message passing distributed system.
%To improve memory locality, we multiplex all connections and event notifications between a pair of threads via one queue.
%We use a high performance shared memory queue for intra-host communication.
%For inter-host communication, we take advantage of modern RDMA hardware, but can also transparently communicate with regular TCP/IP endpoints.
%Together with carefully designed zero-copy mechanism and cooperative multitasking, it removes many overheads of existing socket systems.
%Experiment shows that \sys{} achieves 4 to 24x message throughput, 10 to 60x better latency, and over 40x connection setup throughput compared with Linux socket.


In this paper, we describe \sys, a user-space high performance socket system.
\sys is fully compatible with Linux socket and can be used as a drop-in replacement with no modification to existing applications.
To achieve high performance, \sys{} leverages RDMA and shared memory (共享内存) for inter-host and intra-host communication, respectively.
To bridge the semantics gap between socket and RDMA / 共享内存, we optimize for the common cases while maintaining compatibility in general.
\sys achieves isolation by employing a trusted monitor daemon to handle control plane operations such as connection establishment and access control.
The data plane is peer-to-peer between processes, in which we remove multi-thread synchronization, buffer management, large payload copy and process wakeup overheads in common cases.
Experiments show that \sys achieves 7 to 20x better message throughput and 17 to 35x better latency compared with Linux socket, and reduces Nginx HTTP latency by 5.5 times.
