% !TeX root = ../main.tex

\begin{publications}

\section*{已发表第一作者论文}

\begin{enumerate}
\item \textbf{B. Li}, K. Tan, L. Luo, Y. Peng, R. Luo, N. Xu, Y. Xiong, P. Cheng, E. Chen, ``ClickNP: highly flexible and high performance network processing with reconfigurable hardware'', Proceedings of the 2016 ACM SIGCOMM Conference (\textbf{SIGCOMM '16}), Florianopolis, Brazil, Aug. 2016. （CCF 推荐 A 类会议）
\item \textbf{B. Li}, Z. Ruan, W. Xiao, Y. Lu, Y. Xiong, A. Putnam, E. Chen, L. Zhang, ``KV-direct: High-performance in-memory key-value store with programmable NIC'', Proceedings of the 26th Symposium on Operating Systems Principles (\textbf{SOSP '17}), Shanghai, China, Sept. 2017. （CCF 推荐 A 类会议）
\item \textbf{B. Li}, T. Cui, Z. Wang, W. Bai, L. Zhang, ``SocksDirect: Datacenter Sockets can be Fast and Compatible'', Proceedings of the 2019 ACM SIGCOMM Conference (\textbf{SIGCOMM '19}), Beijing, China, Aug. 2019.（CCF 推荐 A 类会议，已被接收，将于 2019 年 8 月正式出版）
\end{enumerate}

\section*{其他已发表论文}

\begin{enumerate}
\item G. Chen, Y. Lu, Y. Meng, \textbf{B. Li}, K. Tan, D. Pei, P. Cheng, L. Luo, Y. Xiong, X. Wang, Y. Zhao, ``FUSO: Fast Multi-Path loss recovery for data center networks'', IEEE/ACM Transactions on Networking (TON) 2018. (CCF 推荐 A 类期刊)
\item Y. Lu, G. Chen, \textbf{B. Li}, K. Tan, Y. Xiong, P. Cheng, J. Zhang, E. Chen, T. Moscibroda, ``Multi-path transport for RDMA in datacenters'', NSDI 2018. (CCF 推荐 A 类会议)
\item G. Chen, Y. Lu, Y. Meng, \textbf{B. Li}, K. Tan, D. Pei, P. Cheng, L. Luo, Y. Xiong, X. Wang, Y. Zhao, “Fast and Cautious: Leveraging Multi-Path diversity for transport loss recovery in data center”, ATC 2016. (CCF 推荐 A 类会议)
\item Z. Ruan, T. He, \textbf{B. Li}, P. Zhou, J. Cong, “ST-Accel: A high-level programming platform for steaming applications on FPGA”, Proceedings of 26th IEEE International Symposium on Field-Programmable Custom Computing Machines 2018 (FCCM '18). (CCF 推荐 C 类会议)
\item Y. Lu, G. Chen, Z. Ruan, W. Xiao, \textbf{B. Li}, J. Zhang, Y. Xiong, P. Chen, E. Chen, ``Memory efficient loss recovery for hardware-based transport in datacenter'', Proceedings of the 1st Asia-Pacific workshop on networking 2017 (APNet '17).
\item J. Zhang, Y. Xiong, N. Xu, R. Shu, \textbf{B. Li}, P. Cheng, G. Chen, T. Moscibroda, ``The Feniks FPGA Operating System for Cloud Computing'', Proceedings of the 8th Asia-Pacific Workshop on Systems (APSys '17).
\item \textbf{B. Li}, Z. Wang, T. Cui, L. Zhang, ``Fast and Compatible User-Space Container Networking with Programmable NIC'', SOSP Student Research Competition 2017 (poster), Final Presentation Rounds.
\item R. Li, \textbf{B. Li}, G. Zhang, J. Jiang, Y. Luo, ``A High-Performance and Flexible Chemical Structure \& Data Search Engine Built on CouchDB \& ElasticSearch'', Chinese Journal of Chemical Physics, Volume 31, Number 2.
\item J. Meng, H. Tan, C. Xu, W. Cao, L. Liu, \textbf{B. Li}, ``Dedas: Online Task Dispatching and Scheduling with Bandwidth Constraint in Edge Computing'', Proceedings of the 2019 IEEE International Conference on Computer Communications (INFOCOM '19). (CCF 推荐 A 类会议)
\end{enumerate}

\section*{待发表论文}

\begin{enumerate}
\item \textbf{B. Li}, G. Zuo, W. Bai, L. Zhang, ``Efficient and Scalable Total-Order Message Scattering in Data Center Networks''.
\end{enumerate}

%\section*{研究报告}
%\begin{enumerate}
%\item A A A A A A A A A
%\item A A A A A A A A A
%\item A A A A A A A A A
%\end{enumerate}

\end{publications}
